Capstone Movielens Report

### 2025-05-19 reports/capstone-movielens.site/02.5.UME-model.Rmd
Bunch of minor fixes.

::: {.noteblock data-latex=""}
The function described above accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method. We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
We will explain that later in the [User+Movie Effect Model Regularization] section. 
For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. In this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
:::

>>>>

::: {.noteblock data-latex=""}
The function described above accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method. We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
We will explain that later in the [User+Movie Effect Model Regularization] section. 
For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. In this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
:::
